Secure Multi-Party Computation with SCALE-MAMBA

### 2019-04-21 paper.tex
nearly finished

Secure Multi-Party Computation(SMPC) is one possible solution for these use cases. It is a field of research that emerged in the last 30 years, and is gathering a lot of speed in the last years. 

@@

The honest but curious adversary tries to gain as much information as possible while obeying to the rules of the protocol. Hence, it is impossible to know that this party is controlled by a third entity. This adversary tries to retrieve some of the secret information from the other parties, by using all the information he gets during the execution of the protocol.

@@

While this adversary also wants to gain all the information, he is not obeying to the rules of the protocol. This type of adversary can send different inputs to manipulate the results he receives. Furthermore, he wants to interrupt the whole protocol. That could mean making the computation impossible, but as well modifying his own input or his own calculations, so the final result is changed and might lead to different implications
It is important to decide between these two types of adversary, because it shows the different securities SMPC has to guarantee. It has to guarantee that no information is unwillingly shared with an illegal party and at the same time verify that the final result has a correct value. Most SMPC protocols try to guarantee safety versus both type of adveraries, bvut there are also approaches that only use passive security, i.e. only protecting versus non malicious adversaries.

@@

An \((n,t)\)-threshold scheme with \(t<\frac{n}{l}\) means that at least \(t+1\) parties are needed to form a qualified set. Here, \(n\) is the number of total parties, and \(t\) is number of possible adversaries while not revealing any secrets ~\cite{MPCBook_threshold}.\\
A full threshold scheme means that all parties are needed to form a qualified set. This implies, that, if all other parties except one are corrupted by an adversary, this one party can still rely on the fact that it secret remains secret. Of course this has a huge impact on overhead and performance, but in some cases it can provide needed security guarantees.

@@

Choosing the right access structure for the right use case is really important, because it has a realy big impact on performance and on the desired security level.

@@

In the last years, research in SMPC is constantly ongoing, and there are new approaches or improvements to old approaches appearing regulary. But most of these publications only focus on a small area of the whole picture. SCALE-MAMBA\cite{ScaleMambaDocu} is a project that tries to combine the state-of-the-art research into one system. That means that it is offering an end-to-end system for SMPC.\\
It is a research system that is continuously in development, therefore, there is not a single final version that can be examined. It offers a wide range of protocols for different use cases, i.e. it is possible to use the system in different configurations. That also means for this paper, that there is not a single protocol that can be examined. Thus, this paper tries to give more of an overview how the process works in general, which are the main, especially which are newest and best, components and where are the problems and bottlenecks.\\ 
SCALE-MAMBA consists of two parts. One part is called Secure Computation Algorithms from LEuven (SCALE) and is the SMPC part. It contains all the computational logic and algorithms for multi-party computations. The second part is called Multiparty AlgorithMs Basic Argot (MAMBA) and is a compiler for the SMPC programs.\\

In general, the SCALE protocol is split in two parts, first an offline phase and afterwards an online phase. In the online phase only the final evaluation of the function is executed. In the offline phase, prior to the online phase, preparations are done by all the parties to prepare for the evaluation. This includes already calculating values for possible multiplications and MACs, so that the online phase can be executed faster. In this phase the expensive calculations are done, like public key cryptography or authentifications, so that the online phase only needs basic primitives. This phase is not completly offline, because the parties still exchange some information which are later needed for the evaluation. But this phasae is not that time critically, that means it can be already executed a lot earlier than the online phase, so that, when the function evaluation is really needed, the result can be calculated in a rather fast time compared to a system that still has to set up everything. In SCALE-MAMBA, compared to its predecessors, the offline and online phase are completly integrated. Therefore, it is not possible anymore to execute them separately like in SPDZ for example. But it is a much closer approach to a real world application.\\

While SCALE-MAMBA also offers different access structures, the most commonly used security configuration is active security with abort in a full threshold scheme, that means that every except one party could be corrupted, and still no information is leaked, because the evaluation is aborted.

\subsection{MAMBA}
For this paper the more interesting part is the algorithmic part. But still, the importance of the compiler shouldn't be undervalued. Because while the algorthmic foundations might be more important from a theoretical point of view, the compiler, written in C++, enables the user to really use these technologies in a system where he can rely on the security gurantees given by the algorithms. The programs can be written for MAMBA in a syntax similiar to python's. In these programs, the user can specify which security settings he wishes to use. He can specify, how he wants his SMPC to exactly be executed, and which security parameters he wants to use. MAMBA is the compiler which then translates the instruction to bytecode and executes them. MAMBA is the part that gives the system the possibility to be properly used and tested. It makes it easy, to change the parameters, to be able to execute comparable tests, and to have a abstraction level for the user.\\

@@

As mentioned before, SCALE-MAMBA, and in general similiar protocols like SPDZ, use linear secret sharing.\\
Given party \(P_i\) which holds a secret value \( a \in \mathcal{F}_p\) and a share of the global MAC key \( \alpha\). Then \( P_i\) can additvely share \( a\) with the other \(n-1\) parties as follows:
\begin{enumerate}
\item Choose random \(\delta_a \in \mathcal{F}_p\)
\item Compute tag $ \gamma (a)= \alpha(a+\delta)$
\item Choose random \(a_1,...,a_n \in \mathcal{F}_p\) so that $ a=(a_1+...+a_n)$
\item Choose random \((\gamma (a)_1+...+\gamma (a)_n) \in \mathcal{F}_p\) so that $\gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))$
\item Send to each party \( P_j \) \( \delta_a \) and the shares \(a_j \) and, \( \gamma (a)_j \)
\item Now each party \( P_j\) holds a share of \( a\) as tuple \(\langle a_j\rangle = (\delta_a,a_j,\gamma(a)_j )\)
\end{enumerate}

Now the value of \(a\) and the corresponding tag \(\gamma(a)\) can only be reconstructed if, and only if, all \(n\) secret shares are known. At the same time, no bit of information regarding \(a\) is revealed, as long as not all secret shares are known.\\
\textbf{Correctness:} Assume that $n-1$ secret shares are known to an adversary, so all secret shares except one $a_x \in \mathcal{F}_p $. Then the adversary can calculate $\sum_{i \neq x} a_i = a-a_x$. Nevertheless, because $a_x$ was drawn from an independent distribution and the adversary has no information over the value of \(a_x\), knowing $a-a_x$ reveals not a single bit of information about $a$.\\

@@

\textbf{Partial Reveal}
All players send their respective shares of a value, but not the tag share, to one chosen party \(P_i\) which summs up all values and then broadcasts the result. The tag stays secretly shared between the parties.\\
In praxis, the party computing the value is changing for every reveal to keep the workload balanced.\\
\textbf{Full Reveal}
In this case all players broadcast their respective shares and the respective MACs to all players, so all players can calculate the secret and verify the result with the corresponding tag.\\

@@

There are two main things done in the offline phase. The first one is the generation of a global Message Authentification Code(MAC) key $\alpha$. This MAC key is later used, to authenticate the different shares at the end of the computation.\\
The second and and most important part in the offline phase, is the generation of the beaver triples. These triples  are independent of the computation that is later performed in the online phase, but are used in the online phase to express multiplications as a combination of additions and multiplications with constants. For each multiplication, one of the triples is needed.

@@

This algorithm has the disadvantage of high storage complexity, but therefore it doesn't take a long time to calculate and it is symmetric so the same key can be used for creating the tag and verifying it. The symmetry is used for an advantage later on in the protocol.\\

@@

In the offline phase, ZPoKP are used to guarantee that the Beaver triples are calculated correctly before the sacrificing, or atleast that they dont divert more than a specified error \(e\) from the expected result.

ZPoKP are a technique that was introduced  in 1985 \cite{Goldwasser:1985:KCI:22145.22178}. The idea is that one party can prove to another party that it knows a specific value \(x\), without revealing the value of \(x\) to the other person, nor revealing any other knowledge about the value.

@@

\textbf{Correctness:}
Bob wants to prove that \( z\) provided by Alice contains the proper \( x\), so that \( f(x)=y\). 
Because f is homomorphic, obviously \( f(z)=f(s)+f(e*x)=f(s)+e*f(x)=a+e*y\) with \(f(s)=a\) and \(f(x)=y\).
So Bob has to calculate \( a+e*y and f(z)\) with the provided \( z\) by Alice. If they are equal, he knows that Alice knows the \( x\) so that \( f(x)=y\).
He can do that, because he got provided the \( a\) and \( z\) by Alice, he knew the \( y\) before the protocol and he chose the \( e\) himself.\\

@@

\subsubsection{First improvement with MASCOT}
In one of there earlier works, BDOZ, pairwise MACs were used to authentificate the secret sharing between the parties. It used a pairwise multiplication protocol with linear homomorpic encryption. To guarantee the data integritym pairwise zero-knowledge proofs were used, in total O(n2) of them. 
In SPDZ instead of HE, SHE based on the BGV ecnryption scheme was used, reducing the amount of ZK proofs per triple by a factor of n and as well the overhead per triple, because they used a single ZKPoK for proving thousand of triples.
Because the offline phase was the weak point of the existing SPDZ implementations, in regards to runtime while still managing a sufficiently secure system, in 2016 MASCOT \cite{cryptoeprint:2016:505} was introduced, which improved the speed of the offline phase by a magnitude of 2. MASCOT used Oblivious Transfer instead of SHE to significantly reduce the amount of communication and computation. We will not go into detail into this protocol, but rather look on its successor.

>>>>

Secure Multi-Party Computation(SMPC) is one possible solution for these use cases. It is a field of research that emerged within the last 30 years, and is gathering a lot of speed in the last years. 

@@

The honest but curious adversary tries to gain as much information as possible while obeying the rules of the protocol. Hence, it is impossible to know that this party is controlled by a third entity. This adversary tries to retrieve some of the secret information from the other parties, by using all the information he gets during the execution of the protocol.

@@

While this adversary also wants to gain all the information, he is not obeying the rules of the protocol. This type of adversary can send different inputs to manipulate the results he receives. Furthermore, he wants to interrupt the whole protocol. That could mean making the computation impossible, but as well modifying his own input or his own calculations, so the final result is changed and might lead to different implications
It is important to distinguish between these two types of adversary, because it shows the different securities SMPC has to guarantee. It has to guarantee that no information is unwillingly shared with an illegal party and at the same time verify that the final result has a correct value. Most SMPC protocols try to guarantee safety versus both type of adveraries, bvut there are also approaches that only use passive security, i.e. only protecting versus non malicious adversaries.

@@

An \((n,t)\)-threshold scheme with \(t<\frac{n}{l}\) means that at least \(t+1\) parties are needed to form a qualified set. Here, \(n\) is the number of total parties, and \(t\) is the number of possible adversaries while not revealing any secrets ~\cite{MPCBook_threshold}.\\
A full threshold scheme means that all parties are needed to form a qualified set. This implies, that, if all other parties except one are corrupted by an adversary, this one party can still rely on the fact that its secret remains secret. Of course this has a huge impact on overhead and performance, but in some cases it can provide needed security guarantees.

@@

Choosing the right access structure for the right use case is important, because it has a big impact on performance and on the desired security level.

@@

In the last years, research in SMPC is constantly ongoing, and there are new approaches and improvements to old approaches appearing regularly. But most of these publications only focus on a small area of the whole picture. SCALE-MAMBA\cite{ScaleMambaDocu} is a project that tries to combine the state-of-the-art research into one system. That means that it is offering an end-to-end system for SMPC.\\
It is a research system that is continuously in development, therefore, there is not a single final version that can be examined. It offers a wide range of protocols for different use cases, i.e. it is possible to use the system in different configurations. That also means for this paper, that there is not a single protocol that can be examined. Thus, this paper tries to give more of an overview how the process works in general, which are the main, especially newest and best performing, components and where are the problems and bottlenecks.\\ 
SCALE-MAMBA consists of two parts. One part is called Secure Computation Algorithms from LEuven (SCALE) and is the SMPC part. It contains all the computational logic and algorithms for multi-party computations. The second part is called Multiparty AlgorithMs Basic Argot (MAMBA) and is a compiler for the SMPC programs.

In general, the SCALE protocol is split in two parts, first an offline phase and afterwards an online phase. In the online phase only the final evaluation of the function is executed. In the offline phase, prior to the online phase, preparations are done by all parties to prepare for the evaluation. This already includes calculating values for possible multiplications and MACs, so that the online phase can be executed faster. In this phase the expensive calculations are done, like public key cryptography or authentications, so that the online phase only needs basic primitives. The offline phase is not completely offline, because the parties still exchange some information which are later needed for the evaluation. But this phase is not that time critically, that means it can be already executed a lot earlier than the online phase, so that, when the function evaluation is really needed, the result can be calculated in a rather fast time compared to a system that still has to set up everything. In SCALE-MAMBA, compared to its predecessors, the offline and online phase are completely integrated. Therefore, it is not possible anymore to execute them separately like in SPDZ for example. But it is a much closer approach to a real world application.\\

While SCALE-MAMBA also offers different access structures, the most commonly used security configuration is active security with abort in a full threshold scheme, that means that every party except one could be corrupted, and still no information is leaked, because the evaluation is aborted.

\subsection{MAMBA}
For this paper the most interesting part is the algorithmic. But still, the importance of the compiler should not be undervalued. Although the algorithmic foundations might be more important from a theoretical point of view, the compiler, written in C++, enables the user to use these technologies in a system where he can rely on the security guarantees given by the algorithms. The programs can be written for MAMBA in a syntax similar to python's. In these programs, the user can specify which security settings he wishes to use. He can specify, how he wants his SMPC to exactly be executed, and which security parameters he wants to use. MAMBA compiles the instructions to bytecode which is then executed by SCALE. MAMBA is the part that gives the system the possibility to be properly used and tested. It makes it easy to change the parameters, to execute comparable tests, and to have an abstraction level for the user.\\

@@

As mentioned before, SCALE-MAMBA, and in general similiar protocols like SPDZ, use linear secret sharing.\\
Given party \(P_i\) which holds a secret value \( a \in \mathcal{F}_p\) and a share of the global MAC key \( \alpha\). Then \( P_i\) can additvely share \( a\) with the other \(n-1\) parties as follows:
\begin{enumerate}
\item Choose random \(\delta_a \in \mathcal{F}_p\)
\item Compute tag $ \gamma (a)= \alpha(a+\delta)$
\item Choose random \(a_1,...,a_n \in \mathcal{F}_p\) so that $ a=(a_1+...+a_n)$
\item Choose random \((\gamma (a)_1+...+\gamma (a)_n) \in \mathcal{F}_p\) so that $\gamma (a)=((\gamma (a)_1+...+\gamma (a)_n))$
\item Send  \( \delta_a \) and the respective shares \(a_j \) and \( \gamma (a)_j \) to each party \( P_j \) 
\item Now each party \( P_j\) holds a share of \( a\) as tuple \(\langle a_j\rangle = (\delta_a,a_j,\gamma(a)_j )\)
\end{enumerate}

Now the value of \(a\) and the corresponding tag \(\gamma(a)\) can only be reconstructed if, and only if, all \(n\) secret shares are known. At the same time, no bit of information regarding \(a\) is revealed, as long as not all secret shares are known.\\
\textbf{Correctness:} Assume that $n-1$ secret shares are known to an adversary, i.e. all secret shares except one $a_x \in \mathcal{F}_p $. Then the adversary can calculate $\sum_{i \neq x} a_i = a-a_x$. Nevertheless, because $a_x$ was drawn from an independent distribution and the adversary has no information over the value of \(a_x\), knowing $a-a_x$ reveals not a single bit of information about $a$.\\

@@

\textbf{Partial Reveal}
All players send their respective shares of a value, but not the tag share, to one chosen party \(P_i\) which sums up all values and then broadcasts the result. The tag stays secretly shared between the parties.\\
In praxis, the party computing the value is changing for every reveal to keep the workload balanced.\\
\textbf{Full Reveal}
In this case all players broadcast their respective shares and the respective MACs to all players, so all players can calculate the secret and verify the result with the corresponding tag.\\

@@

There are two main things done in the offline phase. The first one is the generation of a global Message Authentication Code(MAC) key $\alpha$. This MAC key is used later, to authenticate the different shares at the end of the computation.\\
The second and and most important part in the offline phase, is the generation of the beaver triples. These triples  are independent of the computation that is later performed in the online phase, but are used in the online phase to express multiplications as a combination of additions and multiplications with constants. For each multiplication, one of the triples is needed.

@@

This algorithm has the disadvantage of high storage complexity because the tag has the same size as the message, which is a difference to other MAC algorithms. But it is symmetric so the same key can be used for creating the tag and verifying it. The symmetry is used for an advantage later on in the protocol.\\

@@

In the offline phase, ZPoKP are used to guarantee that the Beaver triples are calculated correctly before the sacrificing, or at least that they dont divert more than a specified error \(e\) from the expected result.

ZPoKP is a technique that was introduced  in 1985 \cite{Goldwasser:1985:KCI:22145.22178}. The idea is that one party can prove to another party that it knows a specific value \(x\), without revealing the value of \(x\) to the other person, nor revealing any other knowledge about the value.

@@

\textbf{Correctness:}
Bob wants to prove that \( z\) provided by Alice contains the proper \( x\), so that \( f(x)=y\). 
Because f is homomorphic, obviously \( f(z)=f(s)+f(e*x)=f(s)+e*f(x)=a+e*y\) with \(f(s)=a\) and \(f(x)=y\).
So Bob has to calculate \( a+e*y\) and \( f(z)\) with the provided \( z\) by Alice. If they are equal, he knows that Alice knows the \( x\) so that \( f(x)=y\).
He can do that, because he got provided the \( a\) and \( z\) by Alice, he knew the \( y\) before the protocol and he chose the \( e\) himself.\\

@@

\subsubsection{First improvement with MASCOT}
In one of the earlier works, BDOZ, pairwise MACs were used to authentificate the secret sharing between the parties. It used a pairwise multiplication protocol with linear homomorpic encryption. To guarantee the data integritym pairwise zero-knowledge proofs were used, in total O(n2) of them. 
In SPDZ instead of HE, SHE based on the BGV ecnryption scheme was used, reducing the amount of ZK proofs per triple by a factor of n and as well the overhead per triple, because they used a single ZKPoK for proving thousand of triples.
Because the offline phase was the weak point of the existing SPDZ implementations, in regards to runtime while still managing a sufficiently secure system, in 2016 MASCOT \cite{cryptoeprint:2016:505} was introduced, which improved the speed of the offline phase by a magnitude of 2. MASCOT used Oblivious Transfer instead of SHE to significantly reduce the amount of communication and computation. We will not go into detail into this protocol, but rather look on its successor.
